---
title: "Study 1: LP2-Item-level-Prediction"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  github_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE,fig.path = "Study1_item_level/item_")
options(scipen=999)
```


```{r load packages and installize conda environment, include=FALSE}
if (!require("pacman")) install.packages("pacman") #run this if you don't have pacman 
library(pacman)

#setwd("~/Desktop/LP2-within/LP2-intervention-within/Text-Prediction/item_level_analyses")

pacman::p_load(tidyverse,rlang, plotrix, ggpubr, caret, broom, kableExtra, reactable, knitr, DT, stringr,ggwordcloud,Metrics,scales,install = T) 
# Set-up an environment with text-required python packages
```

```{r eval=FALSE, include=FALSE}
library(text)
textrpp_install()
textrpp_initialize()

```

```{r}
plot_aes = theme_minimal() +
  theme(legend.position = "none",
        text = element_text(family = "Futura Medium"),
        axis.ticks.y = element_blank())
```

```{r define functions}
calculate_and_store_rmse <- function(column_name, model_names, actual_values, predicted_values) {
  results_list <- list()
  
  for (col_name in model_names) {
    if (grepl(column_name, col_name)) {
      rmse_value <- Metrics::rmse(actual_values[[column_name]], predicted_values[[col_name]])
      results_list <- c(results_list, list(data.frame(Model = col_name, RMSE = rmse_value)))
    }
  }
  
  return(results_list)
}

# Initialize an empty list to store results
results <- list()


table <- function(correlation_data) {
  # Convert the character columns to factors for better rendering
  correlation_data$descriptions <- gsub("^Q[0-9]+\\.\\.(.+?)\\.\\.Transcription", "\\1", correlation_data$descriptions)
  correlation_data$descriptions <- gsub("(\\d)_([A-Za-z])", "\\1~\\2", correlation_data$descriptions)

  correlation_data$descriptions <- as.factor(correlation_data$descriptions)
  correlation_data$alternative <- as.factor(correlation_data$alternative)
  # Round the numeric columns to three decimal places
  correlation_data$correlation <- round(as.numeric(correlation_data$correlation), 2)
  correlation_data$t_statistics <- round(as.numeric(correlation_data$t_statistics), 3)
  correlation_data$p_value <- sapply(correlation_data$p_value, function(p) {
    ifelse(as.numeric(p) < 0.001, "< .001", 
           ifelse(as.numeric(p) == 1, "1.000", 
                  gsub("0.(.*)", ".\\1", sprintf("%.3f", as.numeric(p)))))
  })
  correlation_data$p_value_corrected <- round(as.numeric(correlation_data$p_value_corrected), 3)

  # Add the RMSE column
  correlation_data$RMSE <- round(as.numeric(correlation_data$RMSE), 2)

  # Create the DataTable
  datatable(correlation_data, extensions = 'FixedColumns', 
            filter = list(position = 'top', clear = FALSE),
            options = list(search = list(regex = TRUE, caseInsensitive = FALSE), pageLength = 25))
}

```

# load data

```{r load-data}


data_dir="/Users/sm9518/Library/CloudStorage/Box-Box/LP2/within_person_intervention"
data <- read_csv(file.path(data_dir,"/data_prediction/surveys_scored/LP2_transcriptions_behavioral.csv"))

df <- data %>%
select(1, starts_with("pre")) %>% 
filter(rowSums(is.na(select(., starts_with("pre")))) == 0) 

embeddings <- read_rds("/Users/sm9518/Library/CloudStorage/Box-Box/LP2/within_person_intervention/data_prediction/embeddings/study_1/all_embeddings.rds")
```

# Inter-item Correlations

```{r}

items = data %>% 
  select(42:63)


calculate_cronbach_alpha <- function(df) {
  # Identify subscales based on column names
  subscales <- unique(sub("_[0-9]+$", "", colnames(df)))
  
  # Remove non-item columns
  subscales <- subscales[!subscales %in% c("pID", "survey_name")]
  
  # Initialize a dataframe to store alpha results
  alpha_results <- data.frame(subscale = character(), alpha = numeric(), stringsAsFactors = FALSE)
  
  # Loop through each subscale and calculate Cronbach's alpha
  for (subscale in subscales) {
    # Select columns for the current subscale
    subscale_cols <- grep(paste0("^", subscale, "_"), colnames(df), value = TRUE)
    
    if (length(subscale_cols) > 0) {
      # Calculate Cronbach's alpha
      alpha_value <- psych::alpha(df[, subscale_cols], check.keys = TRUE)$total$raw_alpha
      
      # Store the result in the dataframe
      alpha_results <- rbind(alpha_results, data.frame(subscale = subscale, alpha = alpha_value))
    }
  }
  
  # Calculate Cronbach's alpha for all PWB items excluding SWLS items
  # Select PWB columns
  pwb_cols <- grep("^PWB_", colnames(df), value = TRUE)
  
  # Select SWLS columns
  swls_cols <- grep("^SWLS_", colnames(df), value = TRUE)
  
  # Ensure there are columns to exclude
  if (length(pwb_cols) > 0 && length(swls_cols) > 0) {
    # Exclude SWLS columns from PWB columns
    pwb_excluding_swls_cols <- setdiff(pwb_cols, swls_cols)
    
    if (length(pwb_excluding_swls_cols) > 0) {
      pwb_alpha_value <- psych::alpha(df[, pwb_excluding_swls_cols], check.keys = TRUE)$total$raw_alpha
      
      # Add the result to the dataframe
      alpha_results <- rbind(alpha_results, data.frame(subscale = "PWB", alpha = pwb_alpha_value))
    }
  }
  
  return(alpha_results)
}


alpha_results <- calculate_cronbach_alpha(items)

pwb = items %>% 
  select(1:18)

pwb_alpha_value = psych::alpha(pwb)$total$raw_alpha
alpha_results <- rbind(alpha_results, data.frame(subscale = "PWB", alpha = pwb_alpha_value))


alpha_results %>% 
  mutate(alpha = round(alpha, 3)) %>% 
  reactable(striped = TRUE,
            filterable = TRUE,
            resizable = TRUE,
            pageSizeOptions = 25)

```


# Models {.tabset}

## Positive Affect {.tabset}

*Prompts*

> Positive Affect 1. Describe a recent time when you felt calm or at ease.

> Positive Affect 2. Describe a recent time when you felt joyful or excited.

> Positive Affect 3. Describe a recent time when you felt interested.

*Qualtrics Questions*

> SWLS 1 In most ways my life is close to my ideal

> SWLS 2 The conditions of my life are excellent

> SWLS 3 I am satisfied with my life

> SWLS 4 So far I have gotten the important things I want in life

> SWLS 5 If I could live my life over, I would change almost nothing

### Models {.tabset}

#### Estimates

```{r}
affect <- df %>%
  select(starts_with("pre_SWLS"))

rds_file_path <- file.path(data_dir, "data_prediction/models/Study-1/Non-Content-Words/Item-level-analyses/affect_item_output.RDS") #update with the path to each model

if (!file.exists(rds_file_path)) {
  affect_item <- textTrainLists(
    x = embeddings$texts[7:9],
    y = affect[1:5],
    force_train_method = "regression",
    save_output = "all",
    method_cor = "pearson",
    eval_measure = "rmse",
    p_adjust_method = "fdr",
    model_description = "positive affect predicting pre-subscales and WB, N = 181",
    multicore = T
  )
   # Save the model output to an RDS file
  saveRDS(affect_item,rds_file_path)
} else {
  # If the RDS file already exists, load the data from it
  affect_item <- readRDS(rds_file_path)
}

affect_item_predictions <-as.data.frame(affect_item$predictions[1:15])
models <- c(colnames(affect_item$predictions[1:15]))


affect_item_predictions <-as.data.frame(affect_item$predictions[1:15])
models <- c(colnames(affect_item$predictions[1:15]))


for (i in 1:5) {
  column_name <- paste0("pre_SWLS_", i)
  result <- calculate_and_store_rmse(
    column_name = column_name,
    model_names = models,
    actual_values = affect,
    predicted_values = affect_item_predictions
  )
  results <- c(results, result)
  # Convert the results list to a data frame
affect_rmse <- results %>%
  bind_rows() %>%
  distinct()
}

affect_item_results <- head(affect_item$results, 15)
affect_item_results$RMSE <- affect_rmse$RMSE
table(affect_item_results)
```  


```{r affect,fig.height=10, fig.width=10}
### Heatmap


affect_item_results$prompt <- str_extract(affect_item_results$descriptions, "^[^_]+")
affect_item_results$SWLS <- str_extract(affect_item_results$descriptions, "[^_]+$")

# Remove the original "descriptions" column
affect_item_results <- affect_item_results %>% 
  select(-descriptions)

affect_item_results$correlation <- as.numeric(affect_item_results$correlation)

affect_item_results <- affect_item_results %>% 
  dplyr:: mutate(prompt = recode(prompt, 
                         "Q1..positive" = "1.Describe a recent time when you felt calm or at ease.",
                         "Q2..positive" = "2.Describe a recent time when you felt joyful or excited.",
                         "Q3..positive" = "3.Describe a recent time when you felt interested."),) %>% 
  dplyr:: mutate(SWLS = recode(SWLS, 
                       "1" = "In most ways my life is close to my ideal",
                       "2" = "The conditions of my life are excellent",
                       "3" = "I am satisfied with my life",
                       "4" = "So far I have gotten the important things I want in life",
                       "5" = "If I could live my life over, I would change almost nothing"))

affect_heat <- ggplot(affect_item_results, aes(x = prompt, y = SWLS, fill = correlation)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(correlation, 2)), color = "black", size = 10) +
  geom_text(aes(label = sprintf("(%s)", round(RMSE, 2))), color = "black", size = 7, vjust = 2) +
  scale_fill_gradient2(low = "dodgerblue",                        
                       mid = "#FFFFCC",                       
                       high = "#c44536") +
    geom_text(data = subset(affect_item_results, p_value_corrected < 0.05), aes(label = "*", x = prompt, y = SWLS, hjust = 1),
              color = "black", size = 10, vjust = -0.5) +
    geom_text(data = subset(affect_item_results, p_value_corrected < 0.01), aes(label = "**", x = prompt, y = SWLS, hjust = 1),
              color = "black", size = 10, vjust = -0.5) +
    geom_text(data = subset(affect_item_results, p_value_corrected < 0.001), aes(label = "***", x = prompt, y = SWLS, hjust = 1),
              color = "black", size = 10, vjust = -0.5) + 
  labs(title = "Positive Affect",x = "prompts", y = "Subscale") + 
  scale_x_discrete(guide = guide_axis(n.dodge = 1),labels = wrap_format(25)) +  
  scale_y_discrete(guide = guide_axis(n.dodge = 1),labels = wrap_format(20)) + 
  plot_aes + 
  theme(plot.title = element_text(hjust = 0.5, vjust = 1.5,size = 24),
        axis.text.x = element_text(size = 16, color = "black"),  
        axis.text.y = element_text(size = 16,color = "black"),
        axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24)) 
  
  

affect_heat 
```


## Purpose {.tabset}

*Prompts*

> Purpose 1. When you think about your life, what are you striving to accomplish?

> Purpose 2. What kind of plans do you have for the future and how are you working towards them?

> Purpose 3. Do you feel like you have a sense of direction in your life, or do you feel like you're wandering aimlessly?

*Qualtrics Questions*

> Purpose 1 Some people wander aimlessly through life, but I am not one of them

> Purpose 2 I live life one day at a time and don't really think about the future

> Purpose 3 I sometimes feel as if I've done all there is to do in life

### Models {.tabset}

#### Estimates

```{r}

purpose <- df %>%
  select(starts_with("pre_Purpose_in_Life"))

rds_file_path <- file.path(data_dir, "data_prediction/models/Study-1/Non-Content-Words/Item-level-analyses/purpose_item_level_output.RDS") #update with the path to each model

if (!file.exists(rds_file_path)) {
 purpose_item <- textTrainLists(
    x = embeddings$texts[10:12],
    y = purpose[1:3],
    force_train_method = "regression",
    save_output = "all",
    method_cor = "pearson",
    eval_measure = "rmse",
    p_adjust_method = "fdr",
    model_description = "purpose predicting pre item-level responses, N = 181",
    multicore = T
  )
  
  
  # Save the model output to an RDS file
  saveRDS(purpose_item, rds_file_path)
} else {
  # If the RDS file already exists, load the data from it
  purpose_item <- readRDS(rds_file_path)
}

###tack on RMSE 

purpose_item_predictions <-as.data.frame(purpose_item$predictions[1:9])
models <- c(colnames(purpose_item$predictions[1:9]))


for (i in 1:3) {
  column_name <- paste0("pre_Purpose_in_Life_", i)
  result <- calculate_and_store_rmse(
    column_name = column_name,
    model_names = models,
    actual_values = purpose,
    predicted_values = purpose_item_predictions
  )
  results <- c(results, result)
  # Convert the results list to a data frame
purpose_rmse <- results %>%
  bind_rows() %>%
  distinct() %>% 
  filter(grepl("Purpose", Model, ignore.case = TRUE))
}
purpose_item_results <- purpose_item$results
purpose_item_results$RMSE <- purpose_rmse$RMSE
table(purpose_item_results)
```

### Heatmap

```{r purpose, fig.height=12, fig.width=12}

purpose_item_results$prompt <- str_extract(purpose_item_results$descriptions, "^[^_]+")
purpose_item_results$purpose <- str_extract(purpose_item_results$descriptions, "[^_]+$")

# Remove the original "descriptions" column
purpose_item_results <- purpose_item_results %>% 
  select(-descriptions)

purpose_item_results$correlation <- as.numeric(purpose_item_results$correlation)


purpose_item_results <- purpose_item_results %>% 
  dplyr:: mutate(prompt = recode(prompt, 
                         "Q1..purpose" = "1.When you think about your life, what are you striving to accomplish?",
                         "Q2..purpose" = "2.What kind of plans do you have for the future and how are you working towards them?",
                         "Q3..purpose" = "3.Do you feel like you have a sense of direction in your life, or do you feel like you're wandering aimlessly?"),) %>% 
  dplyr:: mutate(purpose = recode(purpose, 
                       "1" = "Some people wander aimlessly through life, but I am not one of them",
                       "2" = "I live life one day at a time and don't really think about the future",
                       "3" = "I sometimes feel as if I've done all there is to do in life"))


purpose_heat <- ggplot(purpose_item_results, aes(x = prompt, y = purpose, fill = correlation)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(correlation, 2)), color = "black", size = 12) +
  geom_text(aes(label = sprintf("(%s)", round(RMSE, 2))), color = "black", size = 9, vjust = 2) +
   scale_fill_gradient2(low = "dodgerblue",                        
                       mid = "#FFFFCC",                       
                       high = "#c44536") +
    geom_text(data = subset(purpose_item_results, p_value < 0.05), aes(label = "*", x = prompt, y = purpose, hjust = 1),
              color = "black", size = 12, vjust = -0.5) +
    geom_text(data = subset(purpose_item_results, p_value < 0.01), aes(label = "**", x = prompt, y = purpose, hjust = 1),
              color = "black", size = 12, vjust = -0.5) +
    geom_text(data = subset(purpose_item_results, p_value < 0.001), aes(label = "***", x = prompt, y = purpose, hjust = 1),
              color = "black", size = 12, vjust = -0.5)  + 
  labs(title = "Purpose",x = "prompts", y = "Subscale") + 
  scale_x_discrete(guide = guide_axis(n.dodge = 1),labels = wrap_format(25)) +  
  scale_y_discrete(guide = guide_axis(n.dodge = 1),labels = wrap_format(20)) + 
  plot_aes + 
  theme(plot.title = element_text(hjust = 0.5, vjust = 1.5,size = 24),
        axis.text.x = element_text(size = 16, color = "black"),  
        axis.text.y = element_text(size = 16,color = "black"),
        axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24)) 
  
  
purpose_heat
```

## Relationships {.tabset}

*Prompts*

> Relationships 1. Describe the level of trust between you and your friends.

> Relationships 2. Describe a conversation you had recently with a family member or friends that you enjoyed.

> Relationships 3. Describe a time when you were willing to generously share your time with someone else.

*Qualtrics Questions*

> Relationships 1 Maintaining close relationships has been difficult and frustrating for me

> Relationships 2 People would describe me as a giving person, willing to share my time with others

> Relationships 3 People would describe me as a giving person, willing to share my time with others

### Models {.tabset}

#### Estimates

```{r}
relationships <- df %>%
  select(starts_with("pre_Positive_Relations"))

rds_file_path <- file.path(data_dir, "data_prediction/models/Study-1/Non-Content-Words/Item-level-analyses/relationships_item_level_output.RDS") #update with the path to each model

if (!file.exists(rds_file_path)) {
 relationships_item <- textTrainLists(
    x = embeddings$texts[13:15],
    y = relationships[1:3],
    force_train_method = "regression",
    save_output = "all",
    method_cor = "pearson",
    eval_measure = "rmse",
    p_adjust_method = "fdr",
    model_description = "relationships predicting pre item-level responses, N = 181",
    multicore = T
  )
  
  
  # Save the model output to an RDS file
  saveRDS(relationships_item, rds_file_path)
} else {
  # If the RDS file already exists, load the data from it
  relationships_item <- readRDS(rds_file_path)
}

relationship_item_predictions <-as.data.frame(relationships_item$predictions[1:9])
models <- c(colnames(relationships_item$predictions[1:9]))


for (i in 1:3) {
  column_name <- paste0("pre_Positive_Relations_", i)
  result <- calculate_and_store_rmse(
    column_name = column_name,
    model_names = models,
    actual_values = relationships,
    predicted_values = relationship_item_predictions
  )
  results <- c(results, result)
  # Convert the results list to a data frame
relations_rmse <- results %>%
  bind_rows() %>%
  distinct() %>% 
  filter(grepl("Relations", Model, ignore.case = TRUE))
}


relationships_results <- relationships_item$results
relationships_results$RMSE <- relations_rmse$RMSE

table(relationships_results)
```


### Heatmap

```{r relationships, fig.height=12, fig.width=12}
relationships_results$prompt <- str_extract(relationships_results$descriptions, "^[^_]+")
relationships_results$relationships <- str_extract(relationships_results$descriptions, "[^_]+$")

# Remove the original "descriptions" column
relationships_results <- relationships_results %>% 
  select(-descriptions)

relationships_results$correlation <- as.numeric(relationships_results$correlation)


relationships_results <- relationships_results %>% 
  dplyr:: mutate(prompt = recode(prompt, 
                         "Q1..relationships" = "1.Describe the level of trust between you and your friends.",
                         "Q2..relationships" = "2.Describe a conversation you had recently with a family member or friends that you enjoyed.",
                         "Q3..relationships" = "3.Describe a time you generously share your time with someone else."),) %>% 
  dplyr:: mutate(relationships = recode(relationships, 
                       "1" = "Maintaining close relationships has been difficult and frustrating for me",
                       "2" = "I am willing to share my time with others",
                       "3" = "People would describe me as a giving person"))


relationships_heat <- ggplot(relationships_results, aes(x = prompt, y = relationships, fill = correlation)) +
  geom_tile(color = "white") +
 geom_text(aes(label = round(correlation, 2)), color = "black", size = 12) +
  geom_text(aes(label = sprintf("(%s)", round(RMSE, 2))), color = "black", size = 9, vjust = 2) +
   scale_fill_gradient2(low = "dodgerblue",                        
                       mid = "#FFFFCC",                       
                       high = "#c44536") +
    geom_text(data = subset(relationships_results, p_value_corrected < 0.05), aes(label = "*", x = prompt, y = relationships, hjust = 1),
              color = "black", size = 12, vjust = -0.5) +
    geom_text(data = subset(relationships_results, p_value_corrected < 0.01), aes(label = "**", x = prompt, y = relationships, hjust = 1),
              color = "black", size = 12, vjust = -0.5) +
    geom_text(data = subset(relationships_results, p_value_corrected < 0.001), aes(label = "***", x = prompt, y = relationships, hjust = 1),
              color = "black", size = 12, vjust = -0.5)  + 
  labs(title ="Relationships",x = "prompts", y = "Subscale") + 
  scale_x_discrete(guide = guide_axis(n.dodge = 1),labels = wrap_format(25)) +  
  scale_y_discrete(guide = guide_axis(n.dodge = 1),labels = wrap_format(20)) + 
  plot_aes + 
  theme(plot.title = element_text(hjust = 0.5, vjust = 1.5,size = 24),
        axis.text.x = element_text(size = 16, color = "black"),  
        axis.text.y = element_text(size = 16,color = "black"),
        axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24)) 
  
  
relationships_heat

```

## Self-Acceptance {.tabset}

*Prompts*

> Self-Acceptance 1. What aspect or aspects of your personality do you like?

> Self-Acceptance 2. When you look back at the story of your life, what are you pleased about?

> Self-Acceptance 3. What life achievements are you proud of?

*Qualtrics Questions*

> Self-Acceptance 1 I like most parts of my personality

> Self-Acceptance 2 When I look at the story of my life, I am pleased with how things have turned out so far

> Self-Acceptance 3 In many ways I feel disappointed about my achievements in life

### Models {.tabset}


#### Estimates

```{r}

acceptance <- df %>%
  select(starts_with("pre_Self-Acceptance"))

rds_file_path <- file.path(data_dir, "data_prediction/models/Study-1/Non-Content-Words/Item-level-analyses/acceptance_item_output.RDS") #update with the path to each model


if (!file.exists(rds_file_path)) {
 acceptance_item <- textTrainLists(
    x = embeddings$texts[16:18],
    y = acceptance[1:3],
    force_train_method = "regression",
    save_output = "all",
    method_cor = "pearson",
    eval_measure = "rmse",
    p_adjust_method = "fdr",
    model_description = "acceptance predicting item-level and WB, N = 181",
    multicore = T
  )
  
  
  # Save the model output to an RDS file
  saveRDS(acceptance_item,rds_file_path)
} else {
  # If the RDS file already exists, load the data from it
  acceptance_item <- readRDS(rds_file_path)
}

acceptance_item_predictions <-as.data.frame(acceptance_item$predictions[1:9])
models <- c(colnames(acceptance_item$predictions[1:9]))


for (i in 1:3) {
  column_name <- paste0("pre_Self-Acceptance_", i)
  result <- calculate_and_store_rmse(
    column_name = column_name,
    model_names = models,
    actual_values = acceptance,
    predicted_values = acceptance_item_predictions
  )
  results <- c(results, result)
  # Convert the results list to a data frame
acceptance_rmse <- results %>%
  bind_rows() %>%
  distinct() %>% 
  filter(grepl("Self-Acceptance", Model, ignore.case = TRUE))
}
acceptance_results <- acceptance_item$results
acceptance_results$RMSE <- acceptance_rmse$RMSE
table(acceptance_results)
```

### Heatmap

```{r acceptance, fig.height=12, fig.width=12}
acceptance_results$prompt <- str_extract(acceptance_results$descriptions, "^[^_]+")
acceptance_results$acceptance <- str_extract(acceptance_results$descriptions, "[^_]+$")

# Remove the original "descriptions" column
acceptance_results <- acceptance_results %>% 
  select(-descriptions)

acceptance_results$correlation <- as.numeric(acceptance_results$correlation)

acceptance_results <- acceptance_results %>% 
  dplyr:: mutate(prompt = recode(prompt, 
                         "Q1..self" = "1.What aspect or aspects of your personality do you like?",
                         "Q2..self" = "2.When you look back at the story of your life, what are you pleased about?",
                         "Q3..self" = "3.What life achievements are you proud of?"),) %>% 
  dplyr:: mutate(acceptance = recode(acceptance, 
                       "1" = "I like most parts of my personality",
                       "2" = "When I look at the story of my life, I am pleased with how things have turned out so far",
                       "3" = "In many ways I feel disappointed about my achievements in life"))


acceptance_heat <- 
  ggplot(acceptance_results, aes(x = prompt, y = acceptance, fill = correlation)) +
  geom_tile(color = "white") +
 geom_text(aes(label = round(correlation, 2)), color = "black", size = 12) +
  geom_text(aes(label = sprintf("(%s)", round(RMSE, 2))), color = "black", size = 9, vjust = 2) +
 scale_fill_gradient2(low = "dodgerblue",                        
                       mid = "#FFFFCC",                       
                       high = "#c44536") +
    geom_text(data = subset(acceptance_results, p_value_corrected < 0.05), aes(label = "*", x = prompt, y = acceptance, hjust = 1),
              color = "black", size = 12, vjust = -0.5) +
    geom_text(data = subset(acceptance_results, p_value_corrected < 0.01), aes(label = "**", x = prompt, y = acceptance, hjust = 1),
              color = "black", size = 12, vjust = -0.5) +
    geom_text(data = subset(acceptance_results, p_value_corrected < 0.001), aes(label = "***", x = prompt, y = acceptance, hjust = 1),
              color = "black", size = 12, vjust = -0.5)  + 
  plot_aes + 
  ggtitle("Self-Acceptance") +  
  labs(x = "prompts", y = "Subscale")  +
  scale_x_discrete(guide = guide_axis(n.dodge = 1),labels = wrap_format(25)) +  
  scale_y_discrete(guide = guide_axis(n.dodge = 1),labels = wrap_format(20)) + 
  plot_aes + 
  theme(plot.title = element_text(hjust = 0.5, vjust = 1.5,size = 24),
        axis.text.x = element_text(size = 16, color = "black"),  
        axis.text.y = element_text(size = 16,color = "black"),
        axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24)) 
  



acceptance_heat
```

## Personal Growth {.tabset}

*Prompts*

> Personal Growth 1. What experiences have you had that challenged how you think about yourself and the world?

> Personal Growth 2. How have you developed as a person over time?

> Personal Growth 3. Describe a situation that prompted you to change your old familiar ways of doing things.

*Qualtrics Questions*

> Personal Growth 1 For me, life has been a continuous process of learning, changing, and growth

> Personal Growth 2 I think it is important to have new experiences that challenge how I think about myself and the world

> Personal Growth 3 I gave up trying to make big improvements or changes in my life a long time ago

### Models {.tabset}

#### Estimates

```{r}
growth <- df %>%
  select(starts_with("pre_Personal_Growth"))

rds_file_path <- file.path(data_dir, "data_prediction/models/Study-1/Non-Content-Words/Item-level-analyses/growth_item_output.RDS") #update with

if (!file.exists(rds_file_path)) {
 growth_item <- textTrainLists(
    x = embeddings$texts[4:6],
    y = growth[1:3],
    force_train_method = "regression",
    save_output = "all",
    method_cor = "pearson",
    eval_measure = "rmse",
    p_adjust_method = "fdr",
    model_description = "personal growth predicting item-level and WB, N = 181",
    multicore = T
  )
  
  
  # Save the model output to an RDS file
  saveRDS(growth_item, rds_file_path)
} else {
  # If the RDS file already exists, load the data from it
  growth_item <- readRDS(rds_file_path)
}


growth_item_predictions <-as.data.frame(growth_item$predictions[1:9])
models <- c(colnames(growth_item$predictions[1:9]))

for (i in 1:3) {
  column_name <- paste0("pre_Personal_Growth_", i)
  result <- calculate_and_store_rmse(
    column_name = column_name,
    model_names = models,
    actual_values = growth,
    predicted_values = growth_item_predictions
  )
  results <- c(results, result)
  # Convert the results list to a data frame
growth_rmse <- results %>%
  bind_rows() %>%
  distinct() %>% 
  filter(grepl("Personal_Growth", Model, ignore.case = TRUE))
}

growth_results <- growth_item$results
growth_results$RMSE <- growth_rmse$RMSE
table(growth_results)
```

### Heatmap

```{r growth, fig.height=12, fig.width=12}

growth_results$prompt <- str_extract(growth_results$descriptions, "^[^_]+")
growth_results$growth <- str_extract(growth_results$descriptions, "[^_]+$")

# Remove the original "descriptions" column
growth_results <- growth_results %>% 
  select(-descriptions)

growth_results$correlation <- as.numeric(growth_results$correlation)

growth_results <- growth_results %>% 
  dplyr:: mutate(prompt = recode(prompt, 
                         "Q1..personal" = "1.What experiences have you had that challenged how you think about yourself and the world?",
                         "Q2..personal" = "2.How have you developed as a person over time?",
                         "Q3..personal" = "3.What life achievements are you proud of?"),) %>% 
  dplyr:: mutate(growth = recode(growth, 
                       "1" = "For me, life has been a continuous process of learning, changing, and growth",
                       "2" = "I think it is important to have new experiences that challenge how I think about myself and the world",
                       "3" = "I gave up trying to make big improvements or changes in my life a long time ago"))



growth_heat <- 
ggplot(growth_results, aes(x = prompt, y = growth, fill = correlation)) +
  geom_tile(color = "white") +
 geom_text(aes(label = round(correlation, 2)), color = "black", size = 12) +
  geom_text(aes(label = sprintf("(%s)", round(RMSE, 2))), color = "black", size = 9, vjust = 2) +
 scale_fill_gradient2(low = "dodgerblue",                        
                       mid = "#FFFFCC",                       
                       high = "#c44536") +
    geom_text(data = subset(growth_results, p_value_corrected < 0.05), aes(label = "*", x = prompt, y = growth, hjust = 1),
              color = "black", size = 12, vjust = -0.5) +
    geom_text(data = subset(growth_results, p_value_corrected < 0.01), aes(label = "**", x = prompt, y = growth, hjust = 1),
              color = "black", size = 12, vjust = -0.5) +
    geom_text(data = subset(growth_results, p_value_corrected < 0.001), aes(label = "***", x = prompt, y = growth, hjust = 1),
              color = "black", size = 12, vjust = -0.5) +
  labs(title = "Personal Growth",x = "prompts", y = "Subscale") +  
  scale_x_discrete(guide = guide_axis(n.dodge = 1),labels = wrap_format(25)) +  
  scale_y_discrete(guide = guide_axis(n.dodge = 1),labels = wrap_format(20)) + 
  plot_aes + 
  theme(plot.title = element_text(hjust = 0.5, vjust = 1.5,size = 24),
        axis.text.x = element_text(size = 16, color = "black"),  
        axis.text.y = element_text(size = 16,color = "black"),
        axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24)) 
  
  

growth_heat
```

## Autonomy {.tabset}

*Prompts*

> Autonomy 1. In what ways do you judge yourself by what you think is important and/or what others think is important?

> Autonomy 2. In what ways do you worry about what other people think of you? NOT FEATURED

> Autonomy 3. In what ways are your decisions influenced (or not) by what others are doing?

> Autonomy 4. Describe a time when you chose to voice (or not voice) your own opinion on a controversial matter.

*Qualtrics Questions*

> Autonomy 1 I tend to be influenced by people with strong opinions

> Autonomy 2 I have confidence in my own opinions, even if they are different from the way most other people think

> Autonomy 3 I judge myself by what I think is important, not by the values of what others think is important

### Models {.tabset}

#### Estimates

```{r}

autonomy <- df %>%
  select(starts_with("pre_Autonomy"))


rds_file_path <- file.path(data_dir, "data_prediction/models/Study-1/Non-Content-Words/Item-level-analyses/autonomy_item_output.RDS") #update with


if (!file.exists(rds_file_path)) {
 autonomy_item <- textTrainLists(
    x = embeddings$texts[1:3],
    y = autonomy[1:3],
    force_train_method = "regression",
    save_output = "all",
    method_cor = "pearson",
    eval_measure = "rmse",
    p_adjust_method = "fdr",
    model_description = "autonomy predicting item-level and WB, N = 181",
    multicore = T
  )
  
  
  # Save the model output to an RDS file
  saveRDS(autonomy_item, rds_file_path)
} else {
  # If the RDS file already exists, load the data from it
  autonomy_item <- readRDS(rds_file_path)
}

autonomy_item_predictions <-as.data.frame(autonomy_item$predictions[1:9])
models <- c(colnames(autonomy_item$predictions[1:9]))


for (i in 1:3) {
  column_name <- paste0("pre_Autonomy_", i)
  result <- calculate_and_store_rmse(
    column_name = column_name,
    model_names = models,
    actual_values = autonomy,
    predicted_values = autonomy_item_predictions
  )
  results <- c(results, result)
  # Convert the results list to a data frame
autonomy_rmse <- results %>%
  bind_rows() %>%
  distinct() %>% 
  filter(grepl("autonomy", Model, ignore.case = TRUE))
}

autonomy_results <- autonomy_item$results
autonomy_results$RMSE <- autonomy_rmse$RMSE
table(autonomy_results)
```

### Heatmap

```{r autonomy, fig.height=12, fig.width=12}
autonomy_results$prompt <- str_extract(autonomy_results$descriptions, "^[^_]+")
autonomy_results$autonomy <- str_extract(autonomy_results$descriptions, "[^_]+$")

# Remove the original "descriptions" column
autonomy_results <- autonomy_results %>% 
  select(-descriptions)

autonomy_results$correlation <- as.numeric(autonomy_results$correlation)


autonomy_results <- autonomy_results %>% 
  dplyr:: mutate(prompt = recode(prompt, 
                         "Q1..autonomy" = "1.In what ways do you judge yourself
                         by what you think is important and/or what others think is important?",
                         "Q3..autonomy" = "3.In what ways are your decisions influenced (or not) by what others are doing?",
                         "Q4..autonomy" = "4.Describe a time when you chose to voice (or not voice) your own opinion on a controversial matter."),) %>% 
  dplyr:: mutate(autonomy = recode(autonomy, 
                       "1" = "I tend to be influenced by people with strong opinions",
                       "2" = "I have confidence in my own opinions, even if they are different from the way most other people think",
                       "3" = "I judge myself by what I think is important, not by the values of what others think is important"))

autonomy_heat <- 
  ggplot(autonomy_results, aes(x = prompt, y = autonomy, fill = correlation)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(correlation, 2)), color = "black", size = 12) +
  geom_text(aes(label = sprintf("(%s)", round(RMSE, 2))), color = "black", size = 9, vjust = 2) + # Add RMSE values
  scale_fill_gradient2(low = "dodgerblue",                        
                       mid = "#FFFFCC",                       
                       high = "#c44536") +
  geom_text(data = subset(autonomy_results, p_value_corrected < 0.05), aes(label = "*", x = prompt, y = autonomy, hjust = 1),
            color = "black", size = 12, vjust = -0.5) +
  geom_text(data = subset(autonomy_results, p_value_corrected < 0.01), aes(label = "**", x = prompt, y = autonomy, hjust = 1),
            color = "black", size = 12, vjust = -0.5) +
  geom_text(data = subset(autonomy_results, p_value_corrected < 0.001), aes(label = "***", x = prompt, y = autonomy, hjust = 1),
            color = "black", size = 12, vjust = -0.5) + 
  labs(title = "Autonomy", x = "prompts", y = "Subscale") + 
  scale_x_discrete(guide = guide_axis(n.dodge = 1), labels = wrap_format(25)) +  
  scale_y_discrete(guide = guide_axis(n.dodge = 1), labels = wrap_format(20)) + 
  plot_aes + 
  theme(plot.title = element_text(hjust = 0.5, vjust = 1.5, size = 24),
        axis.text.x = element_text(size = 16, color = "black"),  
        axis.text.y = element_text(size = 16, color = "black"),  # Adjust the margin for y-axis labels
        axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24))

  

autonomy_heat
```


## All heat Maps

```{r all-heat-maps, fig.height=20, fig.width=28}

item_level <- ggarrange(acceptance_heat,autonomy_heat, affect_heat ,purpose_heat,growth_heat,relationships_heat, ncol = 2,nrow = 3, common.legend = F)

item_level +
  ggtitle("Item-Level Predictions") +
  plot_aes  +  
  theme(
    plot.title = element_text(size = 48, hjust = 0.5, vjust = 1.5)
  ) 
```
