---
title: "WBP Study 1: Post-Subscale-level-Prediction"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  github_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE,fig.path = "Post/subscale_")
options(scipen=999)
```


```{r load packages and installize conda environment, include=FALSE}
if (!require("pacman")) install.packages("pacman") #run this if you don't have pacman 
library(pacman)
pacman::p_load(tidyverse,rlang, plotrix, ggpubr, caret, broom, kableExtra, reactable, knitr,DT,stringr,ggwordcloud,Metrics,Rtsne,text,install = T) 

```

```{r eval=FALSE, include=FALSE}
#install.packages("devtools")
#devtools::install_version("text", version = "1.2.1", repos = "http://cran.us.r-project.org")
#### as of 8/29 need to exclusively use version 1.2.1 to get around a fatal R issue
library(text)
textrpp_install(prompt = F)
textrpp_initialize()


```

```{r}
plot_aes = theme_minimal() +
  theme(legend.position = "none",
        legend.text = element_text(size = 6),
        text = element_text(size = 12, family = "Futura Medium"),
        axis.text = element_text(color = "black"),
        axis.ticks.y = element_blank())
```

### functions

```{r define functions}
calculate_and_store_rmse <- function(result_list) {
  results_list <- list()
  
  for (model_name in names(result_list)) {
    # Extract the relevant information from the current result list
    current_result <- result_list[[model_name]]
    
    # Extract observed and predicted values
    observed_values <- current_result$predictions$y
    predicted_values <- current_result$predictions$predictions
    
    # Combine observed and predicted into a data frame to handle NAs
    combined_df <- data.frame(observed = observed_values, predicted = predicted_values)
    
    # Remove rows where either observed or predicted values are NA
    combined_df <- na.omit(combined_df)
    
    # Calculate RMSE only if there are valid pairs left
    if (nrow(combined_df) > 0) {
      rmse_value <- Metrics::rmse(combined_df$observed, combined_df$predicted)
    } else {
      rmse_value <- NA  # Assign NA if no valid pairs exist
    }
    
    # Create a data frame for the current result
    result_df <- data.frame(
      model = model_name,
      RMSE = rmse_value
    )
    
    # Add the data frame to results_list
    results_list <- c(results_list, list(result_df))
  }
  
  # Combine individual data frames into a single data frame
  final_results_df <- do.call(rbind, results_list)
  
  return(final_results_df)
}

# Initialize an empty list to store results
results <- list()


table <- function(correlation_data) {
  # Convert the character columns to factors for better rendering
  correlation_data$model <- as.factor(correlation_data$model)
  correlation_data$method <- as.factor(correlation_data$method)
  correlation_data$data.name <- as.factor(correlation_data$data.name)
  correlation_data$alternative <- as.factor(correlation_data$alternative)

  # Round the numeric columns to three decimal places
  correlation_data$statistic <- round(as.numeric(correlation_data$statistic), 3)
  correlation_data$parameter <- as.integer(correlation_data$parameter)
  correlation_data$p.value <- sapply(correlation_data$p.value, function(p) {
    ifelse(as.numeric(p) < 0.001, "< .001", 
           ifelse(as.numeric(p) == 1, "1.000", 
                  gsub("0.(.*)", ".\\1", sprintf("%.3f", as.numeric(p)))))
  })
  correlation_data$r <- round(as.numeric(correlation_data$r), 3)
  correlation_data$null.value <- round(as.numeric(correlation_data$null.value), 3)
  correlation_data$conf.int_low <- round(as.numeric(correlation_data$conf.int_low), 3)
  correlation_data$conf.int_high <- round(as.numeric(correlation_data$conf.int_high), 3)
  correlation_data$RMSE <- round(as.numeric(correlation_data$RMSE), 3)

  # Create the DataTable
  datatable(correlation_data, extensions = 'FixedColumns', 
            filter = list(position = 'top', clear = FALSE),
            options = list(search = list(regex = TRUE, caseInsensitive = FALSE), pageLength = 25))
}


####use this to create a df for the subscale 
process_results <- function(result_list) {
  results <- data.frame(
    model = character(),
    statistic = numeric(),
    parameter = integer(),
    p.value = numeric(),
    r = numeric(),
    null.value = numeric(),
    alternative = character(),
    method = character(),
    data.name = character(),
    conf.int_low = numeric(),
    conf.int_high = numeric(),
    stringsAsFactors = FALSE
  )

  for (model_name in names(result_list)) {
    # Extract the relevant information from the current data frame
    current_result <- result_list[[model_name]]
    
    # Create a data frame for the current result
    result_df <- data.frame(
      model = model_name,
      statistic = current_result$statistic,
      parameter = current_result$parameter,
      p.value = current_result$p.value,
      r = current_result$estimate,
      null.value = current_result$null.value,
      alternative = current_result$alternative,
      method = current_result$method,
      data.name = current_result$data.name,
      conf.int_low = current_result$conf.int[1],
      conf.int_high = current_result$conf.int[2]
    )
    
    # Add the data frame to autonomy_results
    results <- rbind(results, result_df)
  }

  return(results)
}

```

# load data

```{r load-data}
data_dir="/Users/sm9518/Library/CloudStorage/Box-Box/LP2/"
df = read.csv(file.path(data_dir,"well-being-prediction/data/osf/WBP_Study1_Cleaned.csv"))
df <- df %>%
filter(rowSums(is.na(select(., starts_with("post")))) == 0)
embeddings <- read_rds("/Users/sm9518/Library/CloudStorage/Box-Box/LP2/well-being-prediction/embeddings/Study1_post__embeddings.rds")
model_dir = "/Users/sm9518/Library/CloudStorage/Dropbox/LP2-wellbeing-pred/LP2-wellbeing-prediction/subscale-models-post"
```

# Subscale Predicition {.tabset}

## Autonomy {.tabset}

```{r}
rds_file_path <- file.path(model_dir, "/autonomy/autonomy_subscale_df.RDS") #update with the path to each model
autonomy_path <- file.path(model_dir,"/autonomy")
  

if (!file.exists(rds_file_path)) {
# List all files in the directory with the .RDS extension
rds_files <- list.files(autonomy_path, pattern = "\\.RDS$", full.names = TRUE)

# Load each .RDS file into a separate object
for (autonomy_path in rds_files) {
  # Extract the name (what comes before .RDS)
  name <- tools::file_path_sans_ext(basename(autonomy_path))
  
  # Read the .RDS file
  data <- readRDS(autonomy_path)
  
  # Assign the data to an object with the extracted name
  assign(name, data)
  
}

# Example usage:
result_list <- list(
  autonomy_acceptance_sub = autonomy_acceptance_sub$results,
  autonomy_autonomy_sub = autonomy_autonomy_sub$results,
  autonomy_growth_sub = autonomy_growth_sub$results,
  autonomy_purpose_sub = autonomy_purpose_sub$results,
  autonomy_relationships_sub = autonomy_relationships_sub$results,
  autonomy_PWB_sub = autonomy_PWB_sub$results,
  autonomy_SWLS_sub = autonomy_SWLS_sub$results,
  autonomy_mastery_sub = autonomy_mastery_sub$results
)

autonomy_results <- process_results(result_list)

#calculate RMSE 

result_list <- list(
  autonomy_acceptance_sub = autonomy_acceptance_sub,
  autonomy_autonomy_sub = autonomy_autonomy_sub,
  autonomy_growth_sub = autonomy_growth_sub,
  autonomy_purpose_sub = autonomy_purpose_sub,
  autonomy_relationships_sub = autonomy_relationships_sub,
  autonomy_PWB_sub = autonomy_PWB_sub,
  autonomy_SWLS_sub = autonomy_SWLS_sub,
  autonomy_mastery_sub = autonomy_mastery_sub
)

# Calculate and store RMSE
autonomy_RMSE <- calculate_and_store_rmse(result_list)
autonomy_results$RMSE <- autonomy_RMSE$RMSE

autonomy_results<- 
  autonomy_results %>%
  mutate(
    prompt = ifelse(grepl("autonomy_", model), "autonomy", NA),
    outcome = ifelse(grepl("_sub", model), gsub(".*autonomy_", "", gsub("_sub", "", model)), NA))


# Save the model output to an RDS file
  saveRDS(autonomy_results, rds_file_path)
} else {
  # If the RDS file already exists, load the data from it
  autonomy_results <- readRDS(rds_file_path)
}

```


### Models {.tabset}

#### Estimates 

```{r}
table(autonomy_results)
```

#### Heatmap

```{r fig.height=6, fig.width=6}
autonomy_heat <- ggplot(autonomy_results, aes(x = prompt, y = outcome, fill = r)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(r, 3)), color = "black", size = 4) +
  geom_text(aes(label = sprintf("(%s)", round(RMSE, 3))), color = "black", size = 3, vjust = 2) +  # Add RMSE values

  scale_fill_gradient2(low = "dodgerblue",
                       mid = "#FFFFCC",
                       high = "#c44536") +
    geom_text(data = subset(autonomy_results, p.value < 0.05), aes(label = "*", x = prompt, y = outcome, hjust = 1),
              color = "black", size = 4, vjust = -0.5) +
    geom_text(data = subset(autonomy_results, p.value < 0.01), aes(label = "**", x = prompt, y = outcome, hjust = 1),
              color = "black", size = 4, vjust = -0.5) +
    geom_text(data = subset(autonomy_results, p.value < 0.001), aes(label = "***", x = prompt, y = outcome, hjust = 1),
              color = "black", size = 4, vjust = -0.5) + plot_aes

autonomy_heat
```


## Acceptance {.tabset}

```{r}

rds_file_path <- file.path(model_dir, "acceptance/acceptance_subscale_df.RDS") #update with the path to each model
acceptance_path <- file.path(model_dir,"/acceptance")
  

if (!file.exists(rds_file_path)) {

# List all files in the directory with the .RDS extension
rds_files <- list.files(acceptance_path, pattern = "\\.RDS$", full.names = TRUE)

# Load each .RDS file into a separate object
for (acceptance_path in rds_files) {
  # Extract the name (what comes before .RDS)
  name <- tools::file_path_sans_ext(basename(acceptance_path))
  
  # Read the .RDS file
  data <- readRDS(acceptance_path)
  
  # Assign the data to an object with the extracted name
  assign(name, data)
  
}

result_list <- list(
  accept_acceptance_sub = accept_acceptance_sub$results,
  accept_autonomy_sub = accept_autonomy_sub$results,
  accept_growth_sub = accept_growth_sub$results,
  accept_purpose_sub = accept_purpose_sub$results,
  accept_relationships_sub = accept_relationships_sub$results,
  accept_PWB_sub = accept_PWB_sub$results,
  accept_SWLS_sub = accept_SWLS_sub$results,
  accept_mastery_sub = accept_mastery_sub$results
)
accept_results <- process_results(result_list)

result_list <- list(
accept_acceptance_sub = accept_acceptance_sub,
  accept_autonomy_sub = accept_autonomy_sub,
  accept_growth_sub = accept_growth_sub,
  accept_purpose_sub = accept_purpose_sub,
  accept_relationships_sub = accept_relationships_sub,
  accept_PWB_sub = accept_PWB_sub,
  accept_SWLS_sub = accept_SWLS_sub,
  accept_mastery_sub = accept_mastery_sub)

# Calculate and store RMSE
accept_RMSE <- calculate_and_store_rmse(result_list)
accept_results$RMSE <- accept_RMSE$RMSE

accept_results<- accept_results %>%
  mutate(
    prompt = ifelse(grepl("accept_", model), "accept", NA),
    outcome = ifelse(grepl("_sub", model), gsub(".*accept_", "", gsub("_sub", "", model)), NA))

# Save the model output to an RDS file
  saveRDS(accept_results, rds_file_path)
} else {
  # If the RDS file already exists, load the data from it
  accept_results <- readRDS(rds_file_path)
}

```

### Models {.tabset}

#### Estimates 

```{r}
table(accept_results)
```

#### Heatmap

```{r}
accept_heat <- ggplot(accept_results, aes(x = prompt, y = outcome, fill = r)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(r, 3)), color = "black", size = 4) +
  geom_text(aes(label = sprintf("(%s)", round(RMSE, 3))), color = "black", size = 3, vjust = 2) +  # Add RMSE values
  scale_fill_gradient2(low = "dodgerblue",
                       mid = "#FFFFCC",
                       high = "#c44536") +
    geom_text(data = subset(accept_results, p.value < 0.05), aes(label = "*", x = prompt, y = outcome, hjust = 1),
              color = "black", size = 4, vjust = -0.5) +
    geom_text(data = subset(accept_results, p.value < 0.01), aes(label = "**", x = prompt, y = outcome, hjust = 1),
              color = "black", size = 4, vjust = -0.5) +
    geom_text(data = subset(accept_results, p.value < 0.001), aes(label = "***", x = prompt, y = outcome, hjust = 1),
              color = "black", size = 4, vjust = -0.5) + plot_aes

accept_heat
```

## Affect {.tabset}

### Models {.tabset}

```{r}

rds_file_path <- file.path(model_dir, "affect/affect_results.RDS") #update with the path to each model
affect_path <- file.path(model_dir,"/affect")

if (!file.exists(rds_file_path)) {

# List all files in the directory with the .RDS extension
rds_files <- list.files(affect_path, pattern = "\\.RDS$", full.names = TRUE)

# Load each .RDS file into a separate object
for (affect_path in rds_files) {
  # Extract the name (what comes before .RDS)
  name <- tools::file_path_sans_ext(basename(affect_path))
  
  # Read the .RDS file
  data <- readRDS(affect_path)
  
  # Assign the data to an object with the extracted name
  assign(name, data)
  
}


# Example usage:
result_list <- list(
  affect_acceptance_sub = affect_acceptance_sub$results,
  affect_autonomy_sub =affect_autonomy_sub$results,
  affect_growth_sub = affect_growth_sub$results,
  affect_purpose_sub = affect_purpose_sub$results,
  affect_relationships_sub = affect_relationships_sub$results,
  affect_PWB_sub = affect_PWB_sub$results,
  affect_SWLS_sub = affect_SWLS_sub$results,
  affect_mastery_sub = affect_mastery_sub$results
)
affect_results <- process_results(result_list)



result_list <- list(
  affect_acceptance_sub = affect_acceptance_sub,
  affect_autonomy_sub =affect_autonomy_sub,
  affect_growth_sub = affect_growth_sub,
  affect_purpose_sub = affect_purpose_sub,
  affect_relationships_sub = affect_relationships_sub,
  affect_PWB_sub = affect_PWB_sub,
  affect_SWLS_sub = affect_SWLS_sub,
  affect_mastery_sub = affect_mastery_sub
)

# Calculate and store RMSE
affect_RMSE <- calculate_and_store_rmse(result_list)
affect_results$RMSE <- affect_RMSE$RMSE

affect_results<- affect_results %>%
  mutate(
    prompt = ifelse(grepl("affect_", model), "affect", NA),
    outcome = ifelse(grepl("_sub", model), gsub(".*affect_", "", gsub("_sub", "", model)), NA))


# Save the model output to an RDS file
  saveRDS(affect_results, rds_file_path)
} else {
  # If the RDS file already exists, load the data from it
  affect_results <- readRDS(rds_file_path)
}
```


#### Estimates 

```{r}
table(affect_results)
```


#### Heatmap

```{r fig.height=6, fig.width=6}
affect_heat <- ggplot(affect_results, aes(x = prompt, y = outcome, fill = r)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(r, 3)), color = "black", size = 4) +
  geom_text(aes(label = sprintf("(%s)", round(RMSE, 3))), color = "black", size = 3, vjust = 2) +  # Add RMSE values
  scale_fill_gradient2(low = "dodgerblue",
                       mid = "#FFFFCC",
                       high = "#c44536") +
    geom_text(data = subset(affect_results, p.value < 0.05), aes(label = "*", x = prompt, y = outcome, hjust = 1),
              color = "black", size = 4, vjust = -0.5) +
    geom_text(data = subset(affect_results, p.value < 0.01), aes(label = "**", x = prompt, y = outcome, hjust = 1),
              color = "black", size = 4, vjust = -0.5) +
    geom_text(data = subset(affect_results, p.value < 0.001), aes(label = "***", x = prompt, y = outcome, hjust = 1),
              color = "black", size = 4, vjust = -0.5) + plot_aes

affect_heat
```

## Growth {.tabset}

### Models {.tabset}

```{r}

rds_file_path <- file.path(model_dir, "growth/growth_results.RDS") #update with the path to each model
growth_path <- file.path(model_dir,"/growth")

if (!file.exists(rds_file_path)) {
# List all files in the directory with the .RDS extension
rds_files <- list.files(growth_path, pattern = "\\.RDS$", full.names = TRUE)

# Load each .RDS file into a separate object
for (growth_path in rds_files) {
  # Extract the name (what comes before .RDS)
  name <- tools::file_path_sans_ext(basename(growth_path))
  
  # Read the .RDS file
  data <- readRDS(growth_path)
  
  # Assign the data to an object with the extracted name
  assign(name, data)
  
}


# Example usage:
result_list <- list(
  growth_acceptance_sub = growth_acceptance_sub$results,
  growth_autonomy_sub =growth_autonomy_sub$results,
  growth_growth_sub = growth_growth_sub$results,
  growth_purpose_sub = growth_purpose_sub$results,
  growth_relationships_sub = growth_relationships_sub$results,
  growth_PWB_sub = growth_PWB_sub$results,
  growth_SWLS_sub = growth_SWLS_sub$results,
  growth_mastery_sub = growth_mastery_sub$results
)
growth_results <- process_results(result_list)



result_list <- list(
  growth_acceptance_sub = growth_acceptance_sub,
  growth_autonomy_sub =growth_autonomy_sub,
  growth_growth_sub = growth_growth_sub,
  growth_purpose_sub = growth_purpose_sub,
  growth_relationships_sub = growth_relationships_sub,
  growth_PWB_sub = growth_PWB_sub,
  growth_SWLS_sub = growth_SWLS_sub,
  growth_mastery_sub = growth_mastery_sub
)

# Calculate and store RMSE
growth_RMSE <- calculate_and_store_rmse(result_list)
growth_results$RMSE <- growth_RMSE$RMSE

growth_results<- growth_results %>%
  mutate(
    prompt = ifelse(grepl("growth_", model), "growth", NA),
    outcome = ifelse(grepl("_sub", model), gsub(".*growth_", "", gsub("_sub", "", model)), NA))


# Save the model output to an RDS file
  saveRDS(growth_results, rds_file_path)
} else {
  # If the RDS file already exists, load the data from it
  growth_results <- readRDS(rds_file_path)
}
```


#### Estimates

```{r}
table(growth_results)
```

#### Heatmap

```{r}
growth_heat <- ggplot(growth_results, aes(x = prompt, y = outcome, fill = r)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(r, 3)), color = "black", size = 4) +
  geom_text(aes(label = sprintf("(%s)", round(RMSE, 3))), color = "black", size = 3, vjust = 2) +  # Add RMSE values
  scale_fill_gradient2(low = "dodgerblue",
                       mid = "#FFFFCC",
                       high = "#c44536") +
    geom_text(data = subset(growth_results, p.value < 0.05), aes(label = "*", x = prompt, y = outcome, hjust = 1),
              color = "black", size = 4, vjust = -0.5) +
    geom_text(data = subset(growth_results, p.value < 0.01), aes(label = "**", x = prompt, y = outcome, hjust = 1),
              color = "black", size = 4, vjust = -0.5) +
    geom_text(data = subset(growth_results, p.value < 0.001), aes(label = "***", x = prompt, y = outcome, hjust = 1),
              color = "black", size = 4, vjust = -0.5) + plot_aes

growth_heat
```

## Purpose {.tabset}

```{r}

rds_file_path <- file.path(model_dir, "purpose/purpose_results.RDS") #update with the path to each model
purpose_path <- file.path(model_dir,"/purpose")



if (!file.exists(rds_file_path)) {

# List all files in the directory with the .RDS extension
rds_files <- list.files(purpose_path, pattern = "\\.RDS$", full.names = TRUE)

# Load each .RDS file into a separate object
for (purpose_path in rds_files) {
  # Extract the name (what comes before .RDS)
  name <- tools::file_path_sans_ext(basename(purpose_path))
  
  # Read the .RDS file
  data <- readRDS(purpose_path)
  
  # Assign the data to an object with the extracted name
  assign(name, data)
  
}


# Example usage:
result_list <- list(
  purpose_acceptance_sub = purpose_acceptance_sub$results,
  purpose_autonomy_sub =purpose_autonomy_sub$results,
  purpose_growth_sub = purpose_growth_sub$results,
  purpose_purpose_sub = purpose_purpose_sub$results,
  purpose_relationships_sub = purpose_relationships_sub$results,
  purpose_PWB_sub = purpose_PWB_sub$results,
  purpose_SWLS_sub = purpose_SWLS_sub$results,
  purpose_mastery_sub = purpose_mastery_sub$results
)
purpose_results <- process_results(result_list)



result_list <- list(
  purpose_acceptance_sub = purpose_acceptance_sub,
  purpose_autonomy_sub =purpose_autonomy_sub,
  purpose_growth_sub = purpose_growth_sub,
  purpose_purpose_sub = purpose_purpose_sub,
  purpose_relationships_sub = purpose_relationships_sub,
  purpose_PWB_sub = purpose_PWB_sub,
  purpose_SWLS_sub = purpose_SWLS_sub,
  purpose_mastery_sub = purpose_mastery_sub
)

# Calculate and store RMSE
purpose_RMSE <- calculate_and_store_rmse(result_list)
purpose_results$RMSE <- purpose_RMSE$RMSE

purpose_results<- purpose_results %>%
  mutate(
    prompt = ifelse(grepl("purpose_", model), "purpose", NA),
    outcome = ifelse(grepl("_sub", model), gsub(".*purpose_", "", gsub("_sub", "", model)), NA))


# Save the model output to an RDS file
  saveRDS(purpose_results, rds_file_path)
} else {
  # If the RDS file already exists, load the data from it
  purpose_results <- readRDS(rds_file_path)
}
```

### Models {.tabset}

#### Estimates 
```{r}
table(purpose_results)
```


#### Heatmap

```{r fig.height=6, fig.width=6}
purpose_heat <- ggplot(purpose_results, aes(x = prompt, y = outcome, fill = r)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(r, 3)), color = "black", size = 4) +
  geom_text(aes(label = sprintf("(%s)", round(RMSE, 3))), color = "black", size = 3, vjust = 2) +  # Add RMSE values
  scale_fill_gradient2(low = "dodgerblue",
                       mid = "#FFFFCC",
                       high = "#c44536") +
    geom_text(data = subset(purpose_results, p.value < 0.05), aes(label = "*", x = prompt, y = outcome, hjust = 1),
              color = "black", size = 4, vjust = -0.5) +
    geom_text(data = subset(purpose_results, p.value < 0.01), aes(label = "**", x = prompt, y = outcome, hjust = 1),
              color = "black", size = 4, vjust = -0.5) +
    geom_text(data = subset(purpose_results, p.value < 0.001), aes(label = "***", x = prompt, y = outcome, hjust = 1),
              color = "black", size = 4, vjust = -0.5) + plot_aes

purpose_heat
```


## Relationships {.tabset}

### Models {.tabset}

```{r}

rds_file_path <- file.path(model_dir, "relations/relations_results.RDS") #update with the path to each model
relations_path <- file.path(model_dir,"/relations")

if (!file.exists(rds_file_path)) {
# List all files in the directory with the .RDS extension
rds_files <- list.files(relations_path, pattern = "\\.RDS$", full.names = TRUE)

# Load each .RDS file into a separate object
for (relations_path in rds_files) {
  # Extract the name (what comes before .RDS)
  name <- tools::file_path_sans_ext(basename(relations_path))
  
  # Read the .RDS file
  data <- readRDS(relations_path)
  
  # Assign the data to an object with the extracted name
  assign(name, data)
  
}


# Example usage:
result_list <- list(
  relations_acceptance_sub = relations_acceptance_sub$results,
  relations_autonomy_sub =relations_autonomy_sub$results,
  relations_growth_sub = relations_growth_sub$results,
  relations_purpose_sub = relations_purpose_sub$results,
  relations_relationships_sub = relations_relationships_sub$results,
  relations_PWB_sub = relations_PWB_sub$results,
  relations_SWLS_sub = relations_SWLS_sub$results,
  relations_mastery_sub = relations_mastery_sub$result
)
relations_results <- process_results(result_list)



result_list <- list(
  relations_acceptance_sub = relations_acceptance_sub,
  relations_autonomy_sub =relations_autonomy_sub,
  relations_growth_sub = relations_growth_sub,
  relations_purpose_sub = relations_purpose_sub,
  relations_relationships_sub = relations_relationships_sub,
  relations_PWB_sub = relations_PWB_sub,
  relations_SWLS_sub = relations_SWLS_sub,
  relations_mastery_sub = relations_mastery_sub
)

# Calculate and store RMSE
relations_RMSE <- calculate_and_store_rmse(result_list)
relations_results$RMSE <- relations_RMSE$RMSE

relations_results<- relations_results %>%
  mutate(
    prompt = ifelse(grepl("relations_", model), "relations", NA),
    outcome = ifelse(grepl("_sub", model), gsub(".*relations_", "", gsub("_sub", "", model)), NA))


# Save the model output to an RDS file
  saveRDS(relations_results, rds_file_path)
} else {
  # If the RDS file already exists, load the data from it
  relations_results <- readRDS(rds_file_path)
}
```

#### Estimates 

```{r}
table(relations_results)
```

#### Heatmap

```{r fig.height=6, fig.width=6}
relations_heat <- ggplot(relations_results, aes(x = prompt, y = outcome, fill = r)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(r, 3)), color = "black", size = 4) +
  geom_text(aes(label = sprintf("(%s)", round(RMSE, 3))), color = "black", size = 3, vjust = 2) +  # Add RMSE values
  scale_fill_gradient2(low = "dodgerblue",
                       mid = "#FFFFCC",
                       high = "#c44536") +
    geom_text(data = subset(relations_results, p.value < 0.05), aes(label = "*", x = prompt, y = outcome, hjust = 1),
              color = "black", size = 4, vjust = -0.5) +
    geom_text(data = subset(relations_results, p.value < 0.01), aes(label = "**", x = prompt, y = outcome, hjust = 1),
              color = "black", size = 4, vjust = -0.5) +
    geom_text(data = subset(relations_results, p.value < 0.001), aes(label = "***", x = prompt, y = outcome, hjust = 1),
              color = "black", size = 4, vjust = -0.5) + plot_aes

relations_heat
```

# All subscales Heatmap

```{r all-subscales-heat}


rds_file_path <- file.path(model_dir, "all_subscales.RDS") #update with the path to each model


if (!file.exists(rds_file_path)) {
  
  
combined_df <- rbind(autonomy_results,accept_results, affect_results, growth_results, purpose_results, relations_results)


  saveRDS(combined_df,rds_file_path)
} else {
  # If the RDS file already exists, load the data from it
  combined_df <- readRDS(rds_file_path)
}

combined_df <- combined_df %>%
  mutate(outcome = case_when(
    outcome == "relationships" ~ paste0(outcome, " (PWB)"),
    outcome == "autonomy" ~ paste0(outcome, " (PWB)"),
    outcome == "mastery" ~ paste0(outcome, " (PWB)"),
    outcome == "growth" ~ paste0(outcome, " (PWB)"),
    outcome == "purpose" ~ paste0(outcome, " (PWB)"),
    outcome == "acceptance" ~ paste0(outcome, " (PWB)"),
    TRUE ~ outcome  # This keeps the original value for any other cases
  ))

all_heat <- ggplot(combined_df, aes(x = prompt, y = outcome, fill = r)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(r, 2), 
                fontface = ifelse(p.value < 0.05, "bold", "plain")), 
            color = "black", size = 4) +
  geom_text(aes(label = sprintf("(%s)", round(RMSE, 2))), color = "black", size = 3, vjust = 2) +  # Add RMSE values
  scale_fill_gradient2(low = "dodgerblue",
                       mid = "#FFFFCC",
                       high = "#c44536") +
  geom_text(data = subset(combined_df, p.value < 0.05), 
            aes(label = "*", x = prompt, y = outcome, hjust = 1),
            color = "black", size = 4, vjust = -0.5) +
  geom_text(data = subset(combined_df, p.value < 0.01), 
            aes(label = "**", x = prompt, y = outcome, hjust = 1),
            color = "black", size = 4, vjust = -0.5) +
  geom_text(data = subset(combined_df, p.value < 0.001), 
            aes(label = "***", x = prompt, y = outcome, hjust = 1),
            color = "black", size = 4, vjust = -0.5) + 
  ggtitle("Subscale Prediction") +  plot_aes  +  
  theme(
    plot.title = element_text(hjust = 0.5, vjust = 1.5)
  )
all_heat

```

