---
title: "Study 3: Proliifc LP2 Well-being Prediction"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  github_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE)
options(scipen=999)
```

# load packages
```{r}
if(!require('pacman')) {
	install.packages('pacman')
}

pacman::p_load(tidyverse, devtools, furrr, specr, knitr, kableExtra, psych,install = TRUE)

#devtools::install_github("dcosme/specr", ref = "plotmods")

if (!require(scorequaltrics)) {
  devtools::install_github('dcosme/qualtrics', ref = "dev/enhance")
}

```

# define aesthetics
```{r}
palette = c("#772e25", "#ee9b00", "#197278")
plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 8),
        text = element_text(size = 12, family = "Futura Medium"),
        axis.text = element_text(color = "black"),
        axis.ticks.y = element_blank())
```


# pull qualtrics data {.tabset}
## define variables and paths

To pull data from Qualtrics, you need a credentials file with an API token associated with your account. To create the file, follow these steps.

1. Generate an API token for Qualtrics. Follow the steps outlined [here](https://www.qualtrics.com/support/integrations/api-integration/overview/).

2. Save a Qualtrics credentials text file with the following format. In this example, the file is being saved as `~/credentials.yaml.PENN`. The `baseurl` is the URL for your institution on Qualtrics. Use `upenn.co1.qualtrics.com` for Penn Qualtrics.

```
token: oILNW6...[your qualtrics API token]
baseurl: upenn.co1.qualtrics.com
```

`cred_file_location` = path to your Qualtrics credential file. 

`survey_name_filter` = regular expression to filter the available surveys

```{r}
keep_columns = '(ResponseId|PROLIFIC_PID|order|Finished|Progress|no_consent|failed|)'
cred_file_location = "/Users/stevenmesquiti/Desktop/LP2-within/LP2-text-prediction/LP2-text-prediction/credentials.yaml.PENN" #update with the path to your toke
survey_name_filter = "LP2 well-being prediction PROLIFIC"
ignore_items = "IPAddress|RecipientFirstName|RecipientLastName|RecipientEmail|ExternalReference|LocationLatitude|LocationLongitude"
```

## fetch qualtrics data
The Qualtrics API is pretty finicky. If you get the following error, just rerun the `get_survey_data` command until it works:

```
Error in qualtrics_response_codes(f, raw = TRUE) : 
  Qualtrics API complains that the requested resource cannot be found (404 error).
Please check if you are using the correct survey ID.
```

```{r}
if (!file.exists("../data/Prolific-well-being-prediction.rds")) {
  # load credential file
  credentials = scorequaltrics::creds_from_file(cred_file_location)
  
  # filter
  surveysAvail = scorequaltrics::get_surveys()
  surveysFiltered = filter(surveysAvail, grepl(survey_name_filter, name))
  knitr::kable(arrange(select(surveysFiltered, name), name))
  
  # fetch data
  surveys_long = scorequaltrics::get_survey_data(surveysFiltered,
                                               credentials,
                                               pid_col = keep_columns) %>%
    gather(item, value, -c("survey_name", "ResponseId", "PROLIFIC_PID",
                            "DistributionChannel", "Finished", "Progress", "no_consent"), 
           -contains("failed"), -contains("Date"), -contains("Duration")) %>%
    filter(!grepl(ignore_items, item)) #filter out identifiable data

  saveRDS(surveys_long, "../data/Prolific-well-being-prediction.rds")
} else {
  surveys_long = readRDS("../data/Prolific-well-being-prediction.rds")
}
```

```{r}
###clean up the responses 

surveys_tidy = surveys_long %>%
  filter(!is.na(PROLIFIC_PID)) %>% # remove test responses
  filter(nchar(PROLIFIC_PID) > 1) %>% # remove test responses
  filter(!DistributionChannel == "Preview") %>% # remove incomplete responses
  filter(!grepl("_DO_", item)) %>% # item orders
  filter(!grepl("time_", item)) %>% # timers
  filter(!grepl("Timer_", item)) %>% # timers
  filter(!grepl("UserLanguage|Status", item)) %>%
  filter(Progress >80) %>%
  filter(RecordedDate >= "2024-07-16") # double filter out test cases

### create IDs

ids = surveys_tidy %>%
  select(PROLIFIC_PID) %>%
  unique() %>%
  mutate(pID = sprintf("WBP%03d", row_number())) %>%
  left_join(., unique(select(surveys_tidy, PROLIFIC_PID, ResponseId)))

### attach IDs
data = surveys_tidy %>%
  left_join(., ids) 

data_surveys = data %>%
  filter(Finished == 1) %>%
  filter(!is.na(value)) %>%
  filter(!grepl("Click|Submit|Count|consent|screen|attention|therapy|age|race|ses_|income|practice|hispanic|feedback|first_gen|year|parental", item)) %>%
  filter(grepl("SWLS|PWB|valence|personal|Autonomy|OE|reflection_useful_1|study_exp_helpful", item)) %>%
  select(PROLIFIC_PID, pID,survey_name,item, value) 

###can save this to get the item-level responses

###extract the text data
data_text = data_surveys %>% 
  select(pID,item,value) %>% 
  filter(grepl("-Text", item)) %>% 
  rename(prompt = item,
         text = value)

```

## Score the data 

```{r}
rubric_dir = here::here("/Users/stevenmesquiti/Desktop/LP2-within/LP2-intervention-within/code/scoring_rubrics")
scoring_rubrics = data.frame(file = dir(file.path(rubric_dir), 
                                        pattern = '*.csv',
                                        full.names = TRUE))
scoring_rubrics = scoring_rubrics %>% #filter only the rubrics we need
filter(grepl("SWLS|PWB", file))
# read in rubrics
scoring_data_long = scorequaltrics::get_rubrics(scoring_rubrics, type = 'scoring')

# score
scored = scorequaltrics::score_questionnaire(data_surveys, scoring_data_long, SID = "pID", psych = FALSE) %>%
  rename("pID" = SID) %>%
  mutate(score = as.numeric(score),
         measure = sprintf("%s %s", scale_name, scored_scale)) %>% 
  filter(!method == "sum") %>%
  group_by(measure) %>%
  mutate(score_std = scale(score, center = TRUE, scale = TRUE))


write.csv(scored,"/Users/stevenmesquiti/Box Sync/CurrentProjects_Penn/LP2/well-being-prediction/data/PROLIFIC_LP2_Wellbeing-Prediction_Behavioral.csv")

scored = read_csv('/Users/sm9518/Library/CloudStorage/Box-Box/LP2/well-being-prediction/data/PROLIFIC_LP2_Wellbeing-Prediction_Behavioral.csv')

```

## Tidy Text Data

```{r}

#join behavioral and text data

data = scored %>% 
  right_join(data_text, by = "pID") 

###join itemized tat 

data_item = data_surveys %>% 
  right_join(text, by = "pID") %>% 
  spread(key = prompt, value = text)


# Assuming your dataframe is named 'text'
# Resolve duplicates by grouping and summarizing text values
text_grouped <- data_text %>%
  group_by(pID, prompt) %>%
  summarize(
    text_combined = paste(text, collapse = " "),
    .groups = "drop"  # To avoid keeping group structure
  )

# Reshape data from long to wide format
text_embed <- text_grouped %>%
  spread(key = prompt, value = text_combined)



df = scored %>% 
  select(pID, score, measure) %>% 
   spread(key = measure, value = score)


data_final = df %>% 
  right_join(text_embed, by = "pID")



write.csv(data_final,"/Users/stevenmesquiti/Downloads/Prolific_wellbeing-prediction-text-long.csv")

### write the helpful and usefulness data to a csv... 


help_useful <- data_surveys %>%
  select(pID, Reflection_Type, item, value) %>%
  filter(grepl("study|reflection|OE", item)) %>%
  group_by(pID, Reflection_Type, item) %>%
  summarise(value = first(value)) %>% 
  spread(key = item, value = value)  %>%
  mutate(reflection_useful_1 = as.numeric(reflection_useful_1),
         study_exp_helpful = as.numeric(study_exp_helpful))



#write_csv(help_useful,"/Users/stevenmesquiti/Box Sync/CurrentProjects_Penn/LP2/within_person_intervention/data/WB_help_useful.csv")

```

### demos

```{r}
data_demo = data %>%
  filter(Finished == 1) %>%
  filter(!is.na(value)) %>%
  filter(grepl("gender|age|race|ses-|income|practice|hispanic|feedback|first-|year|parental", item)) %>% 
  filter(!grepl("Click|Submit|Count|consent|screen|attention|therapy|SWLS|PWB|valence|personal|Autonomy|OE|reflection_useful_1|study_exp_helpful|feedback", item)) %>%
  select(PROLIFIC_PID, pID,survey_name,item, value) 



data_demo = demo_study2 %>%
  filter(!is.na(value)) %>%
  filter(!grepl("state", item))

### SES Ladder
ses_subjective = data_demo %>%
  filter(str_starts(item, "ses_subjective") & value == "On") %>% 
  mutate(scale_name = "ses_subjective") %>% 
    select(-value) %>%
  rename("item" = scale_name,
         "value" = item) %>% 
  select(pID, survey_name,item,value) %>% 
  mutate(value = str_replace(value, "ses_subjective_", ""))


### Ethnicity

ethnicity = data_demo %>%
  filter(str_starts(item, "race_ethnicity") & !is.na(value)) %>%
  mutate(item = dplyr::recode(item, 
                              "race_ethnicity_1" = "American Indian or Alaska Native",
                              "race_ethnicity_2" = "Black or African American",
                              "race_ethnicity_3" = "East Asian",
                              "race_ethnicity_4" = "Pacific Islander or Hawaiian Native",
                              "race_ethnicity_5" = "South Asian",
                              "race_ethnicity_6" = "Southeast Asian",
                              "race_ethnicity_7" = "White",
                              "race_ethnicity_8" = "Prefer not to say",
                              "race_ethnicity_9" = "Racial/ethnic identity not listed"), item) %>% 
  mutate(scale_name = "race_ethnicity") %>% 
    select(-value) %>%
  rename("item" = scale_name,
         "value" = item) %>% 
  select(pID, survey_name,item,value)
  


gender = data_demo %>%
  filter(item == "gender" & !is.na(value)) %>%
  mutate(value = dplyr::recode(value, "1" = "Man",
                               "2" = "Woman",
                               "3" = "Prefer not to say",
                               "4" = "Non-binary",
                               "5" = "Genderqueer",
                               "6" = "Agender",
                               "7" = "Gender fluid",
                               "8" = "Gender identity not listed")) %>% 
  select(-survey_name,-item) 


demo = data_demo %>%
  mutate(value = case_when(
    grepl("gender", item) ~ dplyr::recode(value, 
                                          "1" = "Man",
                                          "2" = "Woman",
                                          "3" = "Prefer not to say",
                                          "4" = "Non-binary",
                                          "5" = "Genderqueer",
                                          "6" = "Agender",
                                          "7" = "Gender fluid",
                                          "8" = "Gender identity not listed"),
    grepl("hispanic_latinx", item) ~ dplyr::recode(value, 
                                                   "0" = "No", 
                                                   "1" = "Yes",
                                                   "2" = "Prefer not to say"),
    grepl("transgender", item) ~ dplyr::recode(value, 
                                               "1" = "Yes, man to woman",
                                               "2" = "Yes, woman to man",
                                               "3" = "Yes, man to non-binary",
                                               "4" = "Yes, woman to non-binary",
                                               "0" = "No"),
    grepl("income", item) ~ dplyr::recode(value, 
                                          "1" = "Less than $5,000",
                                          "2" = "$5,000 through $11,999",
                                          "3" = "$12,000 through $15,999",
                                          "4" = "$16,000 through $24,999",
                                          "5" = "$25,000 through $34,999",
                                          "6" = "$35,000 through $49,999",
                                          "7" = "$50,000 through $74,999",
                                          "8" = "$75,000 through $99,999",
                                          "9" = "$100,000 through $149,999",
                                          "10" = "$150,000 and greater",
                                          "11" = "Prefer not to say",
                                          "12" = "NA"),
    grepl("ses-edu", item) ~ dplyr::recode(value, 
                                              "1" = "No formal education",
                                              "2" = "Did not complete high school",
                                              "3" = "High school graduate (diploma)",
                                              "4" = "High school graduate (GED)",
                                              "5" = "Some college (1-4 years, no degree)",
                                              "6" = "Associate's degree (including occupational or academic degrees)",
                                              "7" = "Bachelor's degree (BA, BS, etc)",
                                              "8" = "Master's degree (MA, MS, MENG, MSW, etc)",
                                              "9" = "Professional school degree (MD, DDC, JD, etc)",
                                              "10" = "Doctorate degree (PhD, EdD, etc)"),
    TRUE ~ value  # Default case to keep original value
  )) %>% 
  bind_rows(., ses_subjective, ethnicity) %>%
  arrange(pID)



data_demo_unique <- demo %>%
  group_by(pID, item) %>%
  summarise(value = paste(unique(value), collapse = ", "), .groups = "drop") %>% 
  pivot_wider(names_from = item, values_from = value) %>% 
  mutate(age = as.numeric(age),
         gender = as.factor(gender),
         hispanic_latinx = as.factor(hispanic_latinx),
         race_ethnicity = as.factor(race_ethnicity),
         transgender = as.factor(transgender),
         `ses_degree` = as.factor(`ses-edu`),
         `income` = as.factor(`income`))

```

```{r}
get_demographics_stats <- function(data_demo) {
  # Calculate statistics for age
  age_stats <- list(
    max = max(data_demo$age, na.rm = TRUE),
    min = min(data_demo$age, na.rm = TRUE),
    mean = mean(data_demo$age, na.rm = TRUE),
    sd = sd(data_demo$age, na.rm = TRUE)
  )
  
  # Function to calculate the percentage of each factor level
  get_percentage <- function(column) {
    table <- table(column)
    percentage <- prop.table(table) * 100
    return(as.data.frame(percentage))
  }
  
  # Calculate the percentage of people in each factor level for the specified columns
  first_gen_percentage <- get_percentage(data_demo$`first-gen`)
  gender_percentage <- get_percentage(data_demo$gender)
  hispanic_latinx_percentage <- get_percentage(data_demo$hispanic_latinx)
  race_ethnicity_percentage <- get_percentage(data_demo$race_ethnicity)
  year_college_percentage <- get_percentage(data_demo$`year-college`)
  
  # Create a list to store all results
  results <- list(
    age_stats = age_stats,
    first_gen_percentage = first_gen_percentage,
    gender_percentage = gender_percentage,
    hispanic_latinx_percentage = hispanic_latinx_percentage,
    race_ethnicity_percentage = race_ethnicity_percentage,
    year_college_percentage = year_college_percentage
  )
  
  return(results)
}


demographics_stats <- get_demographics_stats(data_demo_unique)
print(demographics_stats)
```

